Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2015-02-12 draft_lm1.tex
Added presentation.

In this paper we propose a method to bypass the lack of serotype-specific case 
data by informing the time-varying force of infection with the instantaneous 
reproductive number, \rr which we calculate from aggregated data.
The main contribution of this paper can be summarized in the following items: 
(i) we show a method to quantify uncertainty 
about \rr that is readily applicable to other diseases and; (ii) we propose to 
use \rr to inform a dynamic epidemic model with time-varying force of infection 
in order to gain insight into the attack ratio of each epidemic; (iii) We 
propose an estimation procedure for circulating serotype's $S_0$ from 
aggregate case data, which is robust to epidemic sizes; We estimate the AR 
for 18 years of Dengue epidemics.

>>>>

In this paper we propose a method to bypass the lack of serotype-specific case 
data by informing the time-varying force of infection with the instantaneous 
reproductive number, \rr which we calculate from aggregated data.
The main contribution of this paper can be summarized in the following items: 
(i) we show a method to quantify uncertainty 
about \rr that is readily applicable to other diseases and; (ii) we propose to 
use \rr to inform a dynamic epidemic model with time-varying force of infection 
in order to gain insight into the attack ratio of each epidemic; (iii) We 
propose an estimation procedure for circulating serotype's $S_0$ from 
aggregate case data, which is robust to epidemic sizes; (iv) We estimate the AR 
for 18 years of Dengue epidemics.
